\bf Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-07-22 paper.qmd
Added best model with tSNE, updated video link

<!--langevitour with pD model for S-curve-->
<!-- ::: {#fig-scurve-sc layout-ncol="4" fig-pos="H"} -->
<!-- ![](figures/scurve/sc_best_trimesh.png) -->

<!-- ![](figures/scurve/sc_1.png) -->

<!-- ![](figures/scurve/sc_2.png) -->

<!-- ![](figures/scurve/sc_3.png) -->

<!-- XXX Model in \gD{}, on the UMAP layout, and three views of the fit in projections from $7\text{-}D$, for the S-curve data. The model closely fits the shape, but it has breaks which means that it does not adequately capture the surface. (The **langevitour** software is used to view the data with a tour, and the full video is available at <https://youtu.be/N6iWEj3aVps>).  -->
<!-- ::: -->

@@

XXXAdd best fit and discuss why it's the best fit

@@

<!--langevitour with pD model for S-curve--> 
<!-- ::: {#fig-scurve-sc-best layout-ncol="4" fig-pos="H"} -->
<!-- ![](figures/scurve/sc_best_trimap_trimesh.png) -->

<!-- ![](figures/scurve/sc_trimap_best_1.png) -->

<!-- ![](figures/scurve/sc_trimap_best_2.png) -->

<!-- ![](figures/scurve/sc_trimap_best_3.png) -->

<!-- Model in \gD{}, on the TriMAP layout, and three views of the fit in projections from $7\text{-}D$, for the S-curve data. The model closely fits the shape, but it has twists. (The **langevitour** software is used to view the data with a tour, and the full video is available at <https://youtu.be/zEz2MUCtADM>).  -->
<!-- ::: -->

>>>>

<!-- langevitour with pD model for S-curve -->
::: {#fig-scurve-sc layout-ncol="4" fig-pos="H"}
![](figures/scurve/umap_trimesh_layout.png)

![](figures/scurve/sc_1.png)

![](figures/scurve/sc_2.png)

![](figures/scurve/sc_3.png)

Model in \gD{}, on the UMAP layout, and three views of the fit in projections from $7\text{-}D$, for the S-curve data ($(s_1, \ s_2) = (-0.160, \ -0.263)$, $b = 405 \  (15, \ 27)$, $m = 70$, benchmark value to remove low density hexagons is $0.250$, and benchmark value to remove large edges is $0.159$). MSE is $0.0462$. The model closely fits the shape, but it doesn't fully fill out the width of the S, which means that it does not adequately capture the surface (The **langevitour** software is used to view the data with a tour, and the full video is available at <https://youtu.be/N6iWEj3aVps>).
:::

@@

@@

<!-- langevitour with pD model for S-curve -->
::: {#fig-scurve-sc-best layout-ncol="4" fig-pos="H"}
![](figures/scurve/tsne_trimesh_layout.png)

![](figures/scurve/sc_tsne_best_1.png)

![](figures/scurve/sc_tsne_best_2.png)

![](figures/scurve/sc_tsne_best_3.png)

Model in \gD{}, on the tSNE layout, and three views of the fit in projections from $7\text{-}D$, for the S-curve data ($(s_1, \ s_2) = (-0.170, \ -0.137)$, $b = 256 \  (16, \ 16)$, $m = 70$, benchmark value to remove low density hexagons is $0.250$, and benchmark value to remove large edges is $0.180$). MSE is $0.0432$. The model closely fits the shape, but it has some twists (The **langevitour** software is used to view the data with a tour, and the full video is available at <https://youtu.be/ZuLdp89qJ6g>).
:::

### 2024-07-22 paper.tex
Added best model with tSNE, updated video link

@@

XXXAdd best fit and discuss why it's the best fit

>>>>

\begin{minipage}{0.25\linewidth}
\includegraphics{figures/scurve/umap_trimesh_layout.png}\end{minipage}%
%
\begin{minipage}{0.25\linewidth}
\includegraphics{figures/scurve/sc_1.png}\end{minipage}%
%
\begin{minipage}{0.25\linewidth}
\includegraphics{figures/scurve/sc_2.png}\end{minipage}%
%
\begin{minipage}{0.25\linewidth}
\includegraphics{figures/scurve/sc_3.png}\end{minipage}%

\caption{\label{fig-scurve-sc}Model in \gD{}, on the UMAP layout, and
three views of the fit in projections from \(7\text{-}D\), for the
S-curve data (\((s_1, \ s_2) = (-0.160, \ -0.263)\),
\(b = 405 \  (15, \ 27)\), \(m = 70\), benchmark value to remove low
density hexagons is \(0.250\), and benchmark value to remove large edges
is \(0.159\)). MSE is \(0.0462\). The model closely fits the shape, but
it doesn't fully fill out the width of the S, which means that it does
not adequately capture the surface (The \textbf{langevitour} software is
used to view the data with a tour, and the full video is available at
\url{https://youtu.be/N6iWEj3aVps}).}

@@

\begin{minipage}{0.25\linewidth}
\includegraphics{figures/scurve/tsne_trimesh_layout.png}\end{minipage}%
%
\begin{minipage}{0.25\linewidth}
\includegraphics{figures/scurve/sc_tsne_best_1.png}\end{minipage}%
%
\begin{minipage}{0.25\linewidth}
\includegraphics{figures/scurve/sc_tsne_best_2.png}\end{minipage}%
%
\begin{minipage}{0.25\linewidth}
\includegraphics{figures/scurve/sc_tsne_best_3.png}\end{minipage}%

\caption{\label{fig-scurve-sc-best}Model in \gD{}, on the tSNE layout,
and three views of the fit in projections from \(7\text{-}D\), for the
S-curve data (\((s_1, \ s_2) = (-0.170, \ -0.137)\),
\(b = 256 \  (16, \ 16)\), \(m = 70\), benchmark value to remove low
density hexagons is \(0.250\), and benchmark value to remove large edges
is \(0.180\)). MSE is \(0.0432\). The model closely fits the shape, but
it has some twists (The \textbf{langevitour} software is used to view
the data with a tour, and the full video is available at
\url{https://youtu.be/ZuLdp89qJ6g}).}
